Dynein walks like an Imperial AT-ST

### 2018-08-06 papers/paper/paper.tex
Make the paper trajectory plot look prettier

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:trajectory}
\end{figure}

@@

@@

\subsection{Elliott}
\begin{enumerate}
\item Document carefully where all figures and data comes from.
\item Make our cool figures presentable, e.g. trajectory plot.
\item Describe our algorithm in sufficient detail.
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item Update plotting scripts to use stepping analysis python module,
  or other modules.
\item Write up how we estimate one-bound/bothbound time ratio from
  processivity.  Ensure simulation obeys this?
\item Keep trying to get data from Yildiz.
\item Add force-dependent plots to compare with yildiz?
\item Figure out which of the model-em subfigures to include/remove
\end{enumerate}

>>>>

@@

\begin{figure}[tbhp]
\centering
\includegraphics[width=\linewidth]{../../plots/paper_trajectory_plot.pdf}
\caption{\textbf{Model processive trajectory.} \textit{Top view:} x-position of near and far binding domains during a 10 $\mu s$ simulation at high kinetic parameters of $k_b = \trajectorykb s^{-1}$ and $k_{ub} = \trajectorykub s^{-1}$. \textit{Middle view:} Cartoon snapshot of model at time indicated by bottom foot. \textit{Bottom view:} y-projection.}
\label{fig:trajectory}
\end{figure}

@@

\subsection{Elliott}
\begin{enumerate}
\item Document carefully where all figures and data comes from.
\item Make our cool figures presentable, e.g. trajectory plot.
\item Describe our algorithm in sufficient detail.
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item Update plotting scripts to use stepping analysis python module,
  or other modules.
\item Write up how we estimate one-bound/bothbound time ratio from
  processivity.  Ensure simulation obeys this?
\item Keep trying to get data from Yildiz.
\item Add force-dependent plots to compare with yildiz?
\item Figure out which of the model-em subfigures to include/remove
\item add cartoon back to trajectory plot
\end{enumerate}
